Knowledge Representation for Service Robots: Supply and Demand

### 2014-04-16 krs-survey.tex
TRO template (IEEEtran.cls)
Removed Prototypical scenario part

\documentclass[a4paper, twocolumn]{article}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Prototypical Scenario}
\label{sect|scenario}

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{figs/brownie_scenario.jpg}
	\caption{The {\em Brownie} scenario}
	\label{fig|scenario}
\end{figure*}

The aim of this imaginary scenario (that has not been implemented, neither in
simulation nor on a robot) is to materialise early in this paper the context
and challenges of knowledge representation and manipulation for service, social
and interactive robotics. It underlines the place, the role and the need of
knowledge in a near-future, everyday situation where several robots and humans
co-exist and cooperate. This scenario will also be a source of support examples
for later sections of the article. Also, we have emphasised several keywords in
this description: we will come back to them in the next section to
explain them formally and relate them to each other.

We entitle our scenario ``the Brownie scenario'' (Figure~\ref{fig|scenario}):
Robi and Roba are two service robots, that can freely move and pick objects
around (with possibly different hardware and software architectures, including
different knowledge representation systems: typically, two robots built by two
different companies). They cooperate with a human in a kitchen environment.

The main task of the scenario is the joint realization of a brownie, initiated
by Tom, the human: ``Let's make a brownie for tonight!''.

The scenario is successful {\it 1)} if the task is achieved (the brownie is baked),
{\it 2)} in a reasonable time (typically shorter than what it would have been
required by the human alone), {\it 3)} and the human is happy by the help it received
(he/she did not feel useless, uncomfortable, unsafe).

We voluntarily do not detail the subtasks of the scenario, neither we define
how they are shared amongst agents: our focus is on knowledge needs and flows.

A \textit{first order} analysis of this task leads to a rough partition of the
required \emph{representation} abilities:

\begin{enumerate}

	\item Representation abilities related to the execution of a complex
	spatio-temporal task,

	\item Representation abilities related to cooperation with other agents.

\end{enumerate}

% Representation of a complex task
We can further refine these categories: to prepare and bake a brownie, the
robot first needs to make sense of the term \emph{brownie} itself: what is it?
what is it used for? what is it made of? etc. We call this knowledge
\emph{common-sense knowledge} and the robot must be able not only to represent
it, but also to have access to an initial source (for instance through a
initial set of facts that are made available at startup, or via access to a
Web-based knowledge base like Wikipedia)

Once bound to the action \emph{make}, this should lead the robot to build and
represent a \emph{context}: we are in a scenario involving cooking. The context
enables the robot to retrieve more common-sense knowledge, like that actions
related to cooking often take place in the kitchen, cooking requires
ingredients, utensils and a procedure that may be provided by a recipe.

These last assertions imply several other capabilities: ``cooking \emph{often} takes
place in the kitchen'' implies that representation of both uncertainty and
likelihood is desirable. The fact that cooking is associated to a place further
implies that the system models locations and is able to attach \emph{thematic
relations} to concepts (here, the likely location of the cooking action).

``cooking requires a procedure and ingredients'' hints about another important
feature closely tied on knowledge manipulation: \emph{reasoning}. The robot can
\emph{infer} that cooking may require a recipe since a procedure and a list of
ingredients are pre-requisites of the cooking action that may be provided by a
recipe.  If we omit the ``may'', this is a typical example of first-order logic
reasoning.  Many other reasoning techniques exist (including probabilistic ones
-- ones able to deal with the ``may''), we shall illustrate some of them later
in this scenario.

We mentioned that a recipe often provides a procedure (or a \emph{plan}). The
robot should be able to store this plan in a way that allows later execution.
The plan is likely to contain \emph{spatio-temporal constraints} (like ``put
the brownie in the oven for 20 min'' or ``let's cook \emph{for tonight}'') that
must be as well appropriately handled.

To make decision, a robot may also want to \emph{predict} the state of the
world after some action (``if I leave the cake 2h in the oven, it will burn'').
Such ability to project itself in future or, generally speaking, in other
possible state of the world is related to several cognitive ability and
reasoning techniques: \emph{planning}, \emph{projection}, \emph{representation
of possible worlds} and \emph{non-monotonic reasoning}, in addition to
common-sense knowledge and \emph{physics-based} reasoning (that allows for
instance to predict that an egg is likely to break if dropped).

Procedures are in addition often \emph{underspecified}: we can expect the
recipe to provide a cooking duration, but we usually do not expect the recipe
to tell us to first open the oven door, and then put the cake into it, since it
is self-evident that the door must first be opened to put the cake in the oven.
Our cognitive robot should ideally be able to detect and possibly complete such
underspecification.

% Representation feature that enable cooperation
Then, we want our three agents to cooperate. This, in turn, leads to another
set of cognitive abilities.

Cooperation in our scenario can intervene at many places. For instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. This \emph{helping} behaviour makes sense only if
the first agent knows that the recipient agent both needs the information but
does not know it. This in turn requires the robot to be able to access its own
knowledge (\emph{meta-cognition}), as well as to model the knowledge of the
other agents (to think \emph{from the perspective} of another agent, an idea
that is related to the availability of a theory of mind, we will come back to
it later on).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general requires the addresser and the addressee to share a
common interpretative framework (a shared common-sense knowledge -- or cultural
background -- and a shared context). In our scenario, the agents are working in
a kitchen. This element of context does not however suffice if, for example,the 
human asks a robot to ``give {[him]} the bowl''. Behind the symbol
``bowl'', which physical entity are we actually talking about? If we want to
talk and act on the world, this so-called \emph{grounding} operation is
essential. It is a bidirectional process: in covers the {\it top-down}
operation (from the symbol to the percept) and the {\it bottom-up} converse
(retrieval or creation of symbols from perception).

A related ability is called \emph{pre-supposition accommodation}: if one of the
agent moves behind another one, with the brownie dough in its arm, and says
``be careful, I'm behind you!'', we want the first agent to be able to
represent both symbolically and geometrically (because, for instance, if the
agent want to move, it must take into account the new obstacle) something that
is not directly perceived.

Also central to cooperation are the notions of \emph{joint intentions} and
\emph{joint goals}: to help the human during the cooking session, the robots
need to track how far they are into the recipe, what is the next step the human
is likely to go for, how tasks are currently split between agents, what action
is currently blocking the procedure, etc. This knowledge should let the robot
identify the intentions of other agents and create accordingly joint goals.
Hence, a knowledge representation system aiming at dealing with cooperative
behaviours is likely to have goal management structures taking explicitly into
account other agents' actions and goals.

In order to effectively share tasks, the robot must also know what it is
capable of: \emph{capability introspection} (both in term of general capability
and of immediate ability) is thus often desirable. It can be extended to
general introspection (like the ability to tell ``who I am'' or ``what do I
think of'') that may be required for the interaction.

Last but not least, our scenario assumes implicitly \emph{natural interaction}
between humans and robots (as shown by the casual style of the order ``Let's
make a brownie!''), and we want to ensure that the
knowledge available to the robot provides efficient support to the natural
language understanding (for instance by adopting models and vocabulary that are
both well suited for machine processing and remain as close as possible to the
humans own structures and vocabulary), and also to \emph{non-verbal forms of
communication}, like gestures.

>>>>

%\documentclass[a4paper, twocolumn]{article}
\documentclass{IEEEtran}

@@
